\usepackage{glossaries}
\makenoidxglossaries

\newglossaryentry{Android}
{
    name=Android,
    description={Android is a mobile operating system based on a modified version of the Linux kernel and other open source software, designed primarily for touchscreen mobile devices such as smartphones and tablets}
}

\newglossaryentry{Google Play Store}
{
    name=Google Play Store,
    description={Google Play, formerly Android Market, is an American digital distribution service operated and developed by Google. It serves as the official app store for devices running on "Google certified" Android operating system.}
}

\newglossaryentry{Java}
{
    name=Java,
    description={Java is a general-purpose programming language that is class-based, object-oriented, and designed to have as few implementation dependencies as possible. It is intended to let application developers write once, run anywhere (WORA), meaning that compiled Java code can run on all platforms that support Java without the need for recompilation.}
}

\newglossaryentry{Kanban}
{
    name=Kanban Board,
    description={A Kanban board is one of the tools that can be used to implement Kanban to manage work at a personal or organizational level. Kanban boards visually depict work at various stages of a process using cards to represent work items and columns to represent each stage of the process. Cards are moved from left to right to show progress and to help coordinate teams performing the work. A Kanban board may be divided into horizontal "swimlanes" representing different kinds of work or different teams performing the work}
}

\newglossaryentry{Azure Pipelines}
{
    name=Azure Pipelines,
    description={Azure Pipelines is a cloud service that people can use to automatically build and test code project and make it available to other users. Azure Pipelines combines continuous integration (CI) and continuous delivery (CD) to constantly and consistently test and build code and ship it to any target}
}

\newglossaryentry{SonarCloud}
{
    name=SonarCloud,
    description={SonarCloud is the leading product for Continuous Code Quality online, totally free for open-source projects. It supports all major programming languages, including Java, JavaScript, TypeScript, C\#, C++ and many more}
}

\newglossaryentry{Continous Integration and Deployment}
{
    name=Continous Integration and Deployment,
    description={Continuous Integration (CI) is the practice of merging all developers' working copies to a shared mainline several times a day. Continuous deployment (CD) is a software engineering approach in which software functionalities are delivered frequently through automated deployments.}
}

\newglossaryentry{microtransactions}
{
    name=Microtransactions,
    description={Microtransactions are a business model where users can purchase virtual goods with micropayments. Microtransactions are often used in free-to-play games to provide a revenue source for the developers.}
}

\newglossaryentry{add-ons}
{
    name=Add-ons,
    description={A usually commercially distributed add-on for a video game (usually extended story line, new game areas or objects)}
}

\newglossaryentry{GUI}
{
    name=GUI,
    description={Short for Graphical User Interface. A GUI displays objects that convey information, and represent actions that can be taken by the user}
}

\newglossaryentry{PossibleTurn}
{
    name=PossibleTurn,
    description={A possible turn (also called possible move) is an action a player can take during his turn of a round. Generally a player will be able to choose one out of nine possible actions to take, where his car should be moving to}
}

\newglossaryentry{GridPaper}
{
    name=GridPaper,
    description={The overlaying grid put on top of the track during a round of RaceTrack. Players will only be able to move around the grid points provided by the GridPaper}
}

\newglossaryentry{Image}
{
    name=Image,
    description={The actual image which holds the track and starting/finish line. The image defines the track and environment by colors}
}

\newglossaryentry{Track}
{
    name=Track,
    description={The actual track where the cars will drive on. Can be imported by the player from a valid bitmap image. The track defines drivable points, track boundaries and starting/finish line}
}

\newglossaryentry{Start/Finish Line}
{
    name=Start/Finish Line,
    description={Defines the starting and end points of the track}
}

\newglossaryentry{Player}
{
    name=Player,
    description={A player in the game (no NPCs). Each player controls a Car during a race}
}

\newglossaryentry{Car}
{
    name=Car,
    description={A players character, which will be moved around during a race. Are differentiated by different colors}
}

\newglossaryentry{Route}
{
    name=Route,
    description={The past moves of each player will represent its car's route. The route will be represented as a trailing line behind each car}
}

\newglossaryentry{.rtsave}
{
    name=.rtsave,
    description={Special file extension for RaceTrack game files containing various game data, e.g. save games or game configurations}
}